Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-04-21 paper2020/paper.tex
kill more todos

\paragraph{Dynamic Semantics}
Parse trees are then processed by a dynamic semantic component.
Its role is essentially to support  (non-temporal) anaphora, using a
monadic-based dynamic semantics, generally following the state of the
art in this matter
\citep{unger_dynamic_2011,charlow_monadic_2015,charlow_modular_2017}.
Our particular implementation does not handle every case \ifanon
(citations anonymized) \else \citet{bernardy_computational_2020,bernardy_wide-coverage_2019} \fi
but non-temporal anaphoroi in the testsuite are generally resolved as
they should be: on the whole accuracy is not affected significantly by
issues in this subsystem.

@@

We support additionally the basic constructions and phenomena present
in the testsuite, including adjectives, adverbs, nouns, verbs,
anaphora, etc. The method is outlined by
\citet{montague_english_1970,montague_proper_1973}, but we direct the
reader to our previous work for details \ifanon (citations anonymized)
\else \citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019} \fi, but the particular
treatment of such phenomena is essentially independent from our
treatment of time: in this paper we simply ignore these aspects beyond
the fact that they are handled correctly in most of the cases of the
FraCaS testsuite.

@@

In montagovian semantics, (intransitive) verbs are one-place
predicates; in types, they are functions from entities to propositions
($e \to t$).  Our basic approach is to generalise the interpretation of 
verbs, so that it takes two
additional time parameters, one corresponding to the starting time
of the action and one corresponding to its stopping time ($(e × time × time) \to t$). For example,
if John walked between $t_0$ and $t_1$, we would have:
$walk(john,t_0,t_1)$. From now on we will call an interval of time
points $[t_0,t_1]$ a timespan. Every timespan $[t_0,t_1]$ has the
property $t_0 ≤ t_1$ (it starts no later than it stops). (We are thus
using a simple Newtonian model of time, corresponding to a layman
intuition of a linear constant flow of time.)

@@

@@

For the \textit{cognoscenti}, we can already point out some
differences in terminology: we use the term activity as a general term
which encompasses the three classical notions of activites,
achievements and accomplishments. Indeed, insofar as the test suite is
concerned, we find that these three categories can be collapsed into a
single one (they are subject to \cref{eq:unicity}).  As such, we think
it is a good classification, given that it generally affords the
correct inferences for the testsuite. (In this paper, we always assume
that the problems in the FraCaS testsuite are correctly annotated.)

@@

The intros and destruct tactics serve bookkeeping purposes. The
critical part is the use of the \texttt{writeUnique} axiom, which
witnesses the aspectual class of the predicate \texttt{write\_V2}.
The proof is completed by the use of the \texttt{lia} tactic, which is
embeds a decision procedure for linear arithmetic
problems. Fortunately, \texttt{lia} can take care of all the problems
which arise in the FraCaS testsuite.

>>>>

\paragraph{Dynamic Semantics}
Parse trees are then processed by a dynamic semantic component.  Its
role is essentially to support (non-temporal) anaphora, using a
monadic-based dynamic semantics, generally following the state of the
art in this matter
\citep{unger_dynamic_2011,charlow_monadic_2015,charlow_modular_2017}.
Our particular implementation has weaknesses in certain areas (including group readings and counting; see \citet{bernardy_computational_2020} for details)
but non-temporal anaphoroi in the testsuite are generally resolved as
they should be: on the whole accuracy is not affected significantly by
issues in this subsystem.

@@

We support additionally the basic constructions and phenomena present
in the testsuite, including adjectives, adverbs, nouns, verbs,
anaphora, etc. The method is outlined by
\citet{montague_english_1970,montague_proper_1973}, but we direct the
reader to our previous work for details \ifanon (citations anonymized)
\else \citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019} \fi, but the particular
treatment of such phenomena is essentially independent from our
treatment of time: in this paper we simply ignore these aspects beyond
the fact that they are handled correctly in the
FraCaS testsuite, except in a few pathological cases.

@@

In montagovian semantics, (intransitive) verbs are one-place
predicates; in types, they are functions from entities to propositions
($e \to t$).  Our basic approach is to generalise the interpretation of 
verbs, so that it takes two
additional time parameters, one corresponding to the starting time
of the action and one corresponding to its stopping time ($(e × time × time) \to t$). For example,
if John walked between $t_0$ and $t_1$, we would have:
$walk(john,t_0,t_1)$. From now on we will call an interval of time
points $[t_0,t_1]$ a timespan, where $t_0$ and $t_1$ are elements of the $time$ type, which is represented in Coq as an abstract ordered ring. Every timespan $[t_0,t_1]$ has the
property $t_0 ≤ t_1$: it starts no later than it stops. (We are thus
using a simple Newtonian model of time, corresponding to a layman
intuition of a linear constant flow of time.)

@@

\fracasex{271}{\answer unknown
\item	Smith was present.
\item	Jones was present.
\item	Smith was present after Jones was present.
\hyp 	Jones was present before Smith was present.
}

@@

For the \textit{cognoscenti}, we can already point out some
differences in terminology: we use the term activity as a general term
which encompasses the three classical notions of activites,
achievements and accomplishments. Indeed, insofar as the test suite is
concerned, we find that these three categories can be collapsed into a
single one (they are subject to \cref{eq:unicity}).  That is, it is
sufficient for the testsuite to distinguish between events and
states. (In this paper, we always assume that the problems in the
FraCaS testsuite are correctly annotated.)

@@

The intros and destruct tactics serve bookkeeping purposes. The
critical part is the use of the \texttt{writeUnique} axiom, which
witnesses the aspectual class of the predicate \texttt{write\_V2}.
The proof is completed by the use of the \texttt{lia} tactic, which is
embeds a decision procedure for linear arithmetic problems\footnote{It
  solves linear goals over rings by searching for linear refutations
  and cutting planes}. Fortunately, \texttt{lia} can take care of all
the problems which arise in the FraCaS testsuite.
